True versus apparent shapes of astrophysical bow shocks

### 2016-04-08 papers/Paper1/sec-application.tex
Improve figure and caption for circle fit vars

\begin{figure*}
\begin{tabular}{@{}c@{}c@{}c@{}}
  \includegraphics[width=0.33\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-177-341} & \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-177-341} &
  \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-177-341} \\
  \includegraphics[width=0.33\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-LV5} & \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-LV5} &
  \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-LV5} \\
  \includegraphics[width=0.33\linewidth]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-168-328} & 
  \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-168-328} & \includegraphics[width=0.33\linewidth]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-168-328}
\end{tabular}
\label{fig:char-radii-obs}
\caption{Examples of shell's circle fit for three sources:177-341, LV5 and 168-328. In the left side, for each source, the fit is done using all the ds9 marks, while in the middle and the right we show two variations removing a 
fraction of the marks, but always keeping at least four points. 177-341 is an example where the measurementsonly change very slightly from one variation to other. While with 168-328 the changes are a little more noticeable. LV4 is a case where the most external points are crucial
in the determination of the radius of curvature}
\end{figure*}

>>>>

\begin{figure*}
  \setkeys{Gin}{width=0.33\linewidth, trim=10 30 55 62.5}
\begin{tabular}{@{}c@{}c@{}c@{}}

All points & First sub-sample & Second sub-sample \\ \includegraphics[clip]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-177-341} & \includegraphics[clip]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-177-341} &
  \includegraphics[clip]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-177-341} \\
  \includegraphics[clip]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-LV4} & \includegraphics[clip]{../../read-shapes/Multi-Fit/samp05/LV-bowshocks-xyfancy-positionssamp05-LV4} &
  \includegraphics[clip]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-LV4} \\
  \includegraphics[clip]{../../read-shapes/LV-bowshocks-xyfancy-positionswill-168-328} & 
  \includegraphics[clip]{../../read-shapes/Multi-Fit/samp00/LV-bowshocks-xyfancy-positionssamp00-168-328} & \includegraphics[clip]{../../read-shapes/Multi-Fit/samp01/LV-bowshocks-xyfancy-positionssamp01-168-328}
\end{tabular}
\label{fig:char-radii-obs}
\caption{Examples of systematic uncertainties in the circle fits to
  the shell shapes for three sources (top to bottom rows): 177-341,
  LV4 and 168-328.  The left hand column shows the fit to all of the
  points identified on the shell border, where the number and spacing
  of the points is a subjective measure of our confidence in tracing
  the edge of each shell. The remaining two columns show fits to
  randomly selected sub-samples of 2/3 of the points for each shell.}
\end{figure*}

In the better observed shells such as 177-341 (top row), the circle
fits are relatively robust to removing points, resulting in little
variation between the subsamples.

In the left side, for each source, the fit is done using all the ds9
marks, while in the middle and the right we show two variations
removing a fraction of the marks, but always keeping at least four
points. 177-341 is an example where the measurements only change very
slightly from one variation to other. While with 168-328 the changes
are a little more noticeable. LV4 is a case where the most external
points are crucial in the determination of the radius of curvature.
